\documentclass[a4paper,12pt]{article}

% Set the locale for linebreak to Thai
%\XeTeXlinebreaklocale "th"
% In English, when TeX tries to justify text,
% it will add some spaces between words
% For Thai, we "must not" add any space between words
% i.e. put "zero" space beteween words
%\XeTeXlinebreakskip = 0pt plus 0pt
% For a bit better(?) justified output
%\sloppy

% For any unicode characters, require XeTeX/XeLaTeX
\usepackage{fontspec}
\usepackage{subcaption}
\usepackage[document]{ragged2e}
\defaultfontfeatures{Mapping=tex-text} 

% Set main fonts
% For Thai, I recommend to scale the size to the uppercase size of latin alphabet
%\setmainfont[Scale=MatchUppercase,Mapping=tex-text]{TH Sarabun New}
\setmainfont{TeX Gyre Termes}				% Free Times

% Sans font
\setsansfont{TeX Gyre Heros}				% Free Helvetica

% Monospace font
\setmonofont{TeX Gyre Cursor}				% Free Courier
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[top=2cm, bottom=2cm, left=2cm, right=2cm]{geometry}
%\addto{\captionsthai}{\renewcommand{\abstractname}{รายละเอียดของโครงการโดยย่อ}}
\renewcommand{\abstractname}{Project Overview}

% For changing enum label types
\usepackage{enumitem}

\usepackage{amsmath}
\usepackage{listings}
\lstset{
    language=TeX,
    basicstyle=\ttfamily,
    numbers=left,
    numberstyle=\small,
    breaklines=true,
    xleftmargin=.05\linewidth,
    frame=single,
    columns=fullflexible,
    captionpos=b,
    showstringspaces=false,
}



% Any percent sign marks a comment to the end of the line

% Every latex document starts with a documentclass declaration like this
% The option dvips allows for graphics, 12pt is the font size, and article
%   is the style

\usepackage{graphicx}
\usepackage{url}

% These are additional packages for "pdflatex", graphics, and to include
% hyperlinks inside a document.

%\setlength{\oddsidemargin}{0.25in}
%\setlength{\textwidth}{6.5in}
%\setlength{\topmargin}{0in}
%\setlength{\textheight}{8.5in}

\usepackage{authblk}
% Use thai separation for Thai document
%\renewcommand\Authand{ และ }

% IndentFirst line
\usepackage{indentfirst}

% Using hyperlink in document
\usepackage{hyperref}

% Using cleverref for referencing items in the document
\usepackage{cleveref}

% Wrap figure use
\usepackage{wrapfig}

% Table accommodation
%\usepackage{array}
\newcommand*{\thead}[1]{\textbf{#1}}

%Set unnumbered section
\setcounter{secnumdepth}{0}

%Paragraph indentation settings
\setlength{\RaggedRightParindent}{2em}

\begin{document}

% Everything after this becomes content
% Replace the text between curly brackets with your own

\title{Course description\\ \large 988-342 Alternative Energy \& Energy conservation}
\author{Dr. Tanwa Arpornthip}
\date{}

% You can leave out "date" and it will be added automatically for today
% You can change the "\today" date to any text you like
% A blank date can be given if date is not desired in the title

\maketitle
% This command causes the title to be created in the document

\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
\begin{description}
\item [Office] Building 6, ESSAND faculty room
\item [Office Hours] \hfill \\
    Monday 14:00-14:50 Room 5407A \hfill\\
    Friday 12:00-14:00 ESSAND meeting room
\item [Email address] \href{mailto:tanwa.a@phuket.psu.ac.th}{tanwa.a@phuket.psu.ac.th}
\item [Work phone] 076-276-435
\item [Web page] \href{https://lms2.psu.ac.th/course/view.php?id=1025}{https://lms2.psu.ac.th/course/view.php?id=1025}
\item [Class hours] Monday, Wednesday, Friday 16:30-17:30 Room 5407A
\end{description}
\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}

\begin{enumerate}[label=\textbf{\Alph*}]
    \item \textbf{Description} \hfill \\
    The need to better produce, manage, and use energy is undeniable. In this course, we will discuss current energy situations and why we need energy conservation. We will explore why energy conservation alone is not enough and why we need alternative energy. Different types of alternative energy will be discussed: hydroelectric, geothermal, solar, wind, and biomass energy. Future technology will be briefly surveyed. We will studied successful and failure cases of alternative energy deployments. Policies related to alternative energy and energy conservation will be discussed. At the end of the class, students will combine all the knowledge gained throughout the semester to create an alternative energy or energy conservation project proposals for Phuket.
    \item \textbf{Recommended skills} \hfill \\
        Students are not required to have these skills. However, if students find themselves lacking any of these skills, it is highly recommended that appropriate study and/or training are sought for concurrently with the class.
        \begin{itemize}
            \item Although the class will be taught in Thai, ability to read texts in English is highly suggested. As the field of alternative energy is not well-developed in Thailand, most documents will be in English. For example, while a student doesn't need to completely understand this course description, if a student can't grasp the main points of this document without consulting a dictionary, having a productive learning experience will be hard. 
            \item Being able to research for information and present it in a written format in a logical fashion are important in this class. If you have never written a research paper at all in high school, you should look up good research paper examples prior to having to submit one. Some good examples will be presented in the class.
        \end{itemize}
    \item \textbf{Plagiarism} \hfill \\
        Plagiarism is in no way acceptable. A good portion of the class will be dedicated for plagiarism discussion. The use of proper citations are required. Any cases of plagiarism has the following consequence.
        \begin{enumerate}
            \item Students will be informed both verbally and through a written notice about plagiarized cases. Students will have one chance to explain themselves and correct the problem.
            \item A second violation from the same student or a refusal to correct the first violation will result in automatic failure from the class.
            \item Any disputes with the instructor will be arbitrated by a panel of three PSU Phuket lecturers of the student's choosing.
        \end{enumerate}
    \item \textbf{Grade distribution} \hfill \\
    There will be no mid-term or final exams. Instead, students are required to submit the following:
        \begin{tabbing}
            \textbf{Assignments} \hspace{10cm} \=\textbf{Weight} \\
            Class participation \>10\% \\
            Reflection on four example research papers \>5\% \\
            Ten short essays (3-4 pages), including related in-class discussion  \>45\% (4.5\% each) \\
            Project proposal (Groupwork) \>40\% \\
        \end{tabbing}

   The lowest grade out of the ten short essays will be dropped to allow some flexibility.

   \item \textbf{Assignment grading} \hfill \\
   All work will be submitted through \href{https://lms2.psu.ac.th/course/view.php?id=1025}{LMS2} system. \\
   \textbf{Instructor-graded assignments} \hfill \\
   Any requests for re-grade have to be submitted in writing within a week from the date on which an assignment is returned to students, with students' reasoning for the requests clearly stated. Grade adjustment results from a request is considered final. No further requests will be accepted.\\
   \textbf{Peer-graded assignments} \hfill \\
   Peer-graded assignments are done by at least five peers. The graders will be assigned randomly. The lowest and the highest grades from peer graders are dropped. The rest of the grades from peers will be averaged and used as the grade for th assignment. Grading rubrics will be provided for all peer-graded assignments. The instructor reserves the right to override all grades as he sees fit. If an override occurs, the same rule applies for a request for re-grade.
   \item \textbf{Attendance} \hfill \\
   Attendance is \textbf{NOT} required. However, a portion of the final grade comes from class participation. If a student decides to miss a class, it is her own responsibility to hand in any assignments on time and follow-up with class material. With the exception of rare cases, there will not be a make-up class.

   In the rare cases that the instructor has to miss classes, enough reading material will be provided for the students to follow the same schedule posted on \href{https://lms2.psu.ac.th/course/view.php?id=1025}{LMS2}.

   Any changes to the schedule will be announced through \href{https://lms2.psu.ac.th/course/view.php?id=1025}{LMS2} and email.
        
\end{enumerate}

\end{document}
